\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{amscd}
\usepackage{amsfonts}
\usepackage{graphicx}%
\usepackage{fancyhdr}
\usepackage[hmarginratio={1:1},tmargin=2.5cm, scale = 0.8]{geometry}
\usepackage{hyperref} 
\theoremstyle{plain} \numberwithin{equation}{section}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{conjecture}{Conjecture}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{finalremark}[theorem]{Final Remark}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{example}[theorem]{Example}
\newtheorem{question}{Question}



\pagestyle{fancy}\lhead{Curriculum Vitae} 
\chead{{\large{\bf Yiming Zhao}}} \rhead{}\lfoot{} \rfoot{\bf \thepage} \cfoot{}

\newcounter{list}


\begin{document}

%\begin{center}
%{\large {\bf \ CURRICULUM VITAE for Name} }
%\end{center}

\large{\textbf{Contact Information}}

\medskip

\begin{tabular}{ll}

Address: & Department of Mathematics\\
  & Syracuse University\\
  & 130 Sims Dr.\\
  & 215 Carnegie library \\
  & Syracuse, NY 13244\\
E-mail: & \href{mailto:yzhao197@syr.edu}{yzhao197@syr.edu}\\
URL: & \href{https://www.yimingzhao.net}{yimingzhao.net}\\

\end{tabular}

\bigskip

{\large\textbf{Education}}
\medskip

\begin{tabular}{ll}
2012--2017 & \textbf{Ph.D. in Mathematics}, New York University, New York, U.S.\\
& Adviser: Erwin Lutwak, Deane Yang, and Gaoyong Zhang\\
& Thesis: Geometric measures, affine invariants, \\
&\phantom{qweqwe}and their characterizations\\
2007--2011 & \textbf{B.S. in Mathematics}, Shanghai University, Shanghai, China\\
\end{tabular} \medskip


{\large\textbf{Research Interests}\\} \medskip
\begin{tabular}{lll}
&&convex geometry, geometric analysis, partial differential equations
\end{tabular} \medskip

{\large\textbf{Employment}}
\medskip

\begin{tabular}{ll}
2021 -- & Assistant Professor\\
&\phantom{qwewae} at Syracuse University\\

2018 --	2021	& C.L.E. Moore Instructor\\
&\phantom{qwewae} at Massachusetts Institute of Technology\\
& Mentor: David Jerison\\
2017 -- 2018 &  Assistant Professor (non-tenure track)\\
 &\phantom{qwewae} at St. John's University\\
Summer 2017 & Research Associates \& Adjunct Assistant Professor\\
&\phantom{qwewae} at New York University\\
\end{tabular} \medskip

{\large\textbf{Grant}}


\begin{itemize}
		\item NSF CAREER Grant DMS-2337630 (sole PI), 06/2024 --- 05/2029, \$434,697.00
		\item NSF Grant DMS-2002778, DMS-2132330 (sole PI), 06/2020 --- 05/2024, \$159,159.00
\end{itemize}

{\large\textbf{Publications and Preprints}}

\begin{enumerate}
\item (with D. Xi) Fractional affine area measures, \emph{submitted} in 2024.
\item (with V. Semenov) The growth rate of surface area measure for noncompact convex sets with prescribed asymptotic cone, \emph{Transactions of the American Mathematical Society}, 378 (11): 7945-7975, 2025.
\item (with D. Langharst and M. Roysdon) On the $m$-th order affine P\'olya-Szeg\"o principle, \emph{Journal of Geometric Analysis}, 35 (7): Paper No. 205, 32pp, 2025.
\item (with N. Fang, D. Ye, and Z. Zhang) Dual Orlicz curvature measures for log-concave functions and their Minkowski problems, \emph{Calculus of Variations and Partial Differential Equations}, 64: Paper No. 44, 31pp, 2025.
\item (with Y. Huang, J. Liu, and D. Xi) Dual curvature measures for log-concave functions, \emph{Journal of Differential Geometry}, 128 (2): 815-860, 2024.
\item (with L. Guo and D. Xi) The $L_p$ chord Minkowski problem in a critical interval. \emph{Mathematische Annalen}, 389: 3123-3162, 2024.
\item (with S. Chen, S. Hu, and W. Liu) On the planar Gaussian-Minkowski problem, \emph{Advances in Mathematics}, Volume 435, Part A: 109351, 32pp, 2023.
\item (with D. Xi, D. Yang, and G. Zhang) The $L_p$ chord Minkowski problem, \emph{Advanced Nonlinear Studies}, 23: pp. 20220041, 2023.
\item (with D. Xi) General affine invariances related to Mahler volume, \textit{International Mathematics Research Notices}, 2022: 14151-14180, 2022. 
\item (with Y. Huang and D. Xi) The Minkowski problem in Gaussian probability space, \textit{Advances in Mathematics}, 385: Paper No. 107769, 36 pp, 2021.
\item (with K. B\"{o}r\"{o}czky, E. Lutwak, D. Yang, and G. Zhang) The Gauss image problem, \textit{Communications on Pure and Applied Mathematics}, 73: 1406-1452, 2020.
\item (with K. B\"{o}r\"{o}czky, E. Lutwak, D. Yang, and G. Zhang) The dual Minkowski problem for symmetric convex bodies, \textit{Advances in Mathematics}, 356:106805, 2019.
\item The $L_p$ Aleksandrov problem for origin-symmetric polytopes, \textit{Proceedings of the American Mathematical Society}, 147 (10): 4477-4492, 2019.
\item (with C. Chen, and Y. Huang) Smooth solutions to the $L_p$-dual Minkowski problem, \textit{Mathematische Annalen}, 373 (3-4):953-976, 2019.
\item (with Y. Huang) On the $L_p$ dual Minkowski problem, \textit{Advances in Mathematics}, 332: 57-84, 2018.
 
\item Existence of solutions to the even dual Minkowski problem. \textit{Journal of Differential Geometry}, 110 (3): 543-572, 2018.

\item The dual {M}inkowski problem for negative indices. \textit{Calculus of Variations and Partial Differential Equations}, 56 (2):18, 2017.

\item On {$L_p$}-affine surface area and curvature measures. \textit{International Mathematics Research Notices}, (5): 1387--1423, 2016.



\end{enumerate}

{\large\textbf{Invited Talks}}
\begin{itemize}
\item 2025 Oct. AMS Fall Central Sectional Meeting at St. Louis. Affine area measures.
\item 2024 Dec. MFO--Oberwolfach workshop ``Convex Geometry and its Applications'' at Oberwolfach, Germany. Growth rate of surface area measures for $C$-asymptotic sets.
\item 2024 May. Convex Geometry and Related PDEs conference at Changsha, China. On the geometry of log-concave functions.
\item 2023 Dec. Winter meeting of Canadian Mathematical Society at Montreal. The Minkowski problem in Gaussian probability space.
\item 2023 Dec. Beijing Technology and Business University (virtual).  The Minkowski problem in Gaussian probability space. 
\item 2023 Jun. INdAM Meeting ``Convex Geometry - Analytic Aspects'' at Cortona, Italy. The Minkowski problem in Gaussian probability space. (\textbf{main speaker})
\item 2023 Jun. Summer Meeting of Canadian Mathematical Society at Ottawa. The Minkowski problem in Gaussian probability space.
\item 2023 May. Southwest University (virtual). The dual Minkowski problem. (3-hour short lecture)
\item 2023 May. Chinese Academy of Sciences (virtual). The Minkowski problem in Gaussian probability space.
\item 2022 Dec. Shanghai University (virtual). Dual curvature measures for log-concave functions.
\item 2022 Dec. Beihang University (virtual). Dual curvature measures for log-concave functions.
\item 2022 Dec. Shanxi Normal University (virtual). Dual curvature measures for log-concave functions.
\item 2022 Nov. Cornell University. Dual curvature measures for log-concave functions.
\item 2022 Sep. ICERM. Dual curvature measures for log-concave functions.
\item 2021 Sep. Syracuse University. Mass transport problem on the unit sphere via Gauss map.
\item 2021 May  Jilin Normal University (virtual). Mass transport problem on the unit sphere via Gauss map.
\item 2021 Mar. Syracuse University (virtual, colloquium). Recovering the shapes of convex bodies.
\item 2021 Feb. Florida International University (virtual, colloquium). Recovering the shapes of convex bodies.
\item 2021 Feb. University of Georgia (virtual, colloquium). Recovering the shapes of convex bodies.
\item 2021 Jan. UC San Diego (virtual).  Mass transport problem on the unit sphere via Gauss map. 
\item 2021 Jan. UC Santa Cruz (virtual, colloquium). Recovering the shapes of convex bodies.
\item 2020 Oct.  AMS special session (virtual)
, The Minkowski problem in Gaussian probability space.
\item 2020 Aug. University of Connecticut (virtual), Reconstruction of convex bodies via Gauss map.
\item 2019 Jun. International Congress of Chinese Mathematicians, 45-min talk, The dual Minkowski problem for $o$-symmetric convex bodies.
\item 2019 Jun. Fudan University, The dual Minkowski problem for $o$-symmetric convex bodies.
\item 2019 Jun. Tongji University, The dual Minkowski problem for $o$-symmetric convex bodies.
\item 2019 Jun. Shanghai University, The dual Minkowski problem for $o$-symmetric convex bodies.
\item 2019 Jun. Hunan University, lecture series: An Introduction to Minkowski-type problems in convex geometry.
\item 2019 May. AIM workshop, The even dual  Minkowski problem for integer indices.
\item 2019 Jan. University of Connecticut, PDE and Differential Geometry Seminar: The Gauss image problem. 
\item 2018 Mar. AMS special session at Ohio State University, The Aleksandrov problem and its recent development.
\item 2017 Dec. St. John’s University, Minkowski problems and Monge-Amp\`{e}re type equations.
\item 2017 Sept. CUNY Graduate Center, Geometric Analysis Seminar: Minkowski-type problems in convex geometry.
\item 2017 Feb. Case Western Reserve University, Analysis \& Probability Seminar: On the dual Minkowski problem.
\item 2017 Feb. Kent State University, Measure Theory Seminar: The dual Minkowski problem and its solution.
\item 2015 Sep. Oaxaca, Mexico (CMO workshop): On {$L_p$}-affine surface area and curvature measures. 
\end{itemize}

{\large\textbf{Courses Taught}}

\begin{itemize}
\item Syracuse University

\begin{tabular}{rll}
Fall & 2025: &MAT-296 Calculus II\\
&& MAT-512 Introduction to Real Analysis II\\
Spring &2025:  &MAT-412 Introduction to Real Analysis I\\
& & MAT-800 Topics in Analysis\\
&& \phantom{sdasdsada} An introduction to convex geometric analysis\\
Fall &2024: &on research leave\\
Spring &2024: &MAT-602 Fundamentals of Analysis II\\
Fall &2023:  &MAT-412 Introduction to Real Analysis I\\
Spring &2023:  &MAT-602 Fundamentals of Analysis II\\
Fall & 2022: &MAT-512 Introduction to Real Analysis II\\
Spring & 2022: & MAT-296 Calculus II\\
Fall & 2021: & MAT-296 Calculus II
\end{tabular}
\item Massachusetts Institute of Technology

\begin{tabular}{rll}
Spring & 2021: & 18.02 Calculus (recitation leader)\\
Fall & 2020: & 18.100Q Communication Intensive Real Analysis\\
Spring & 2020: & 18.03 Differential Equations (recitation leader)\\
Fall & 2019: & 18.100Q Communication Intensive Real Analysis\\
Spring & 2019: & 18.03 Differential Equations (recitation leader)\\
Fall & 2018: & 18.01A/18.02A Calculus (recitation leader)
\end{tabular}

\item St. John's University

\begin{tabular}{rll}
Spring &2018: & MTH-1260 Pharmacy Calculus; MTH-1320 Business Calculus\\
Fall & 2017: & MTH-1250 Pharmacy Statistics; MTH-1300 College Algebra
\end{tabular}
\end{itemize}

{\large\textbf{Professional Services}}

\begin{itemize}

	\item[-] \textbf{Grant review}
	\item NSF panelist, 2026.
	\item NSF ad-hoc reviewer, 2025.
	\item[-]\textbf{Committee services}
	\item Graduate Committee, Syracuse University, Fall 2025 -- present
	\item External Ph.D. thesis examiner for Xia Zhou, Memorial University of Newfoundland, Canada, Summer 2025
	\item External Ph.D. thesis examiner for Wen Ai, Memorial University of Newfoundland, Canada, Spring 2025
	\item Ph.D. thesis defense committee member for Jesse Hulse, Syracuse University, Spring 2025
	\item Applied Math hiring committee, Syracuse University, Fall 2023
	\item Probability hiring committee, Syracuse University, Fall 2022
	\item[-] \textbf{Conference/workshop organization}

	\item Co-organizer of the \emph{Algebra Workshop for MAT-295}, Syracuse University, Fall 2025 -- present.
	
	In recent years, there has been a nation-wide trend of more students struggling with Calculus courses due to weak background in algebra. Literature shows that a remedial prerequisite course in algebra might not be particularly effective. 

	This workshop is designed to provide students enrolled in MAT-295 Calculus I at Syracuse University with \emph{just-in-time} algebra support. The idea is to have students brush up their relevant algebra skills to be used in the next Calculus Lecture. The workshop is co-organized by Pawel Grzegrzolka and myself, and led by an undergraduate student.

	\item Co-organizer of the \emph{Analysis Seminar}, Syracuse University, March 2025 -- present.

	\item Co-organizer of the AMS Special Session on \emph{Probabilistic and Analytic Aspects in Convexity}, October 2024.
	\item Co-organizer of the Special Session \emph{Interplay Between Analysis and Convexity} in the 2023 Summer Meeting of the Canadian Mathematical Society
	
	
	\item[-] \textbf{Journal referee}
		\item[]I refereed/provided quick opinion \emph{multiple times} for the following journals: \emph{Advances in Applied Mathematics, Advances in Geometry,
Advances in Mathematics, Advanced Nonlinear Studies, Bulletin des sciences math\'ematiques Calculus of Variations and Partial Differential Equations, Discrete and Continuous Dynamical Systems Series S, Indagationes Mathematicae, International Mathematics Research Notices, Journal of Differential Geometry, Journal of Differential Equations, Journal of Geometric Analysis, Journal of Mathematical Analysis and Applications, Journal of the European Mathematical Society, Mathematische Annalen, Nonlinear Analysis, Proceedings of the American Mathematical Society, Rocky Mountain Journal of Mathematics, SCIENCE CHINA Mathematics, Transactions of the American Mathematical Society.}

I also write reviews for \emph{MathSciNet} and \emph{zbMATH}.
\item[-]Community service

\item Professional development mini-course for local high school teachers, \emph{From Shape Discovery to Daily Life: bees cats, engineering, medicine, ...}, October--November, 2025.

I developed and taught a mini-course for local high school teachers in the central NYS area.
	
	This mini-course was attended by around 25 local high school teachers. It conveys my research to high school teachers in an accessible way. The goal is to show the teachers (and consequently their students) that Mathematics is much more than a set of formulas, and that just like any other sciences, one can explore, discover, and experiment in Mathematics.

\item  Presenter of the ``Be the Scientist'' program at the \emph{Milton J. Rubenstein Museum of Science and Technology} (MOST) in Syracuse, NY, May, 2025.

\item Together with Dr. Ruth Chen and Cory Monahan, we designed and supervised a community outreach program that provided  Grade 2--8 students (most of which from under-represented population) at \emph{the North Side Learning Center} weekly fun problems in Mathematics that intend to expose the fun and exploratory side of Mathematics to students early in their educational career. This program took place during the months of July and August, 2024. 
\end{itemize}

{\large\textbf{Graduate student advising}}
\begin{itemize}
	\item Cory Monahan
	\item Xinfa Meng
\end{itemize}


{\large\textbf{Post-doc mentoring}}

Sudan Xing, 2023, currently Assistant Professor at University of Arkansas at Little Rock
 
\end{document}
